Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-12-07 paper/main.Rmd
definitions added

## Idea

@@

### Algorithm

Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets. Let the pairwise distances between combinations be denoted as $d_{(j,k), (j', k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$. If $b_{k} = b_{k'}$, distances considered are within-facet. Otherwise they are between-facet.

```{r distance-explain, fig.cap = "Mapping to data space to graphic space shown. Cyclic granularity A is mapped to x-axis and B is mapped to facets and the dotted lines represent the distances between different categories. Panel 1) and 2) show the between-facet distances. Panel 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively. When categories are ordered, distances should only be considered for consecutive x-axis categories. Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}."}
knitr::include_graphics(here::here("paper/Figs/dist_explain.png"))
```

The maximum weighted pairwise distances are defined as:
$$MEPD = max_{j, j', k, k'}(d*_{(j,k), (j', k')})
\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$
where,

\begin{equation}
d*_{(j,k), (j', k')} =
\begin{cases}
\lambda * d_{(j,k), (j', k')},& \text{if } b_{k} = b_{k'}\\
(1-\lambda) * d_{(j,k), (j', k')},              & \text{otherwise}
\end{cases}
\end{equation}

>>>>

## Idea {#sec:idea}

@@

### Methodology

Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets. Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}, b_{k})$ be denoted as $d_{(jk, j', k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$. Pairwise distances could be within-facets or between-facets. Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined. Pairwise distances are within-facets ($d_{w}$) when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}. If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where $a_{j'} = (a_{j+1})$ are considered (panel (4)). Pairwise distances are between-facets ($d_{b}$) when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.

```{r distance-explain, fig.pos="p", fig.cap = "Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets. The dotted lines represent the distances between different categories. Panel 1) and 2) show the between-facet distances. Panel 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively. When categories are ordered, distances should only be considered for consecutive x-axis categories. Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}."}
knitr::include_graphics(here::here("paper/Figs/dist_explain.png"))
```

From Section \ref{sec:idea}, the idea is to put more weightage on within-facet distances than between-facet distances. Hence, for a suitable tuning parameter $\lambda > 1$, the pairwise distances $d_{(jk, j'k')}$ are transformed based on the distance type as follows:

\begin{equation}
d*_{(j,k), (j'k')} =
\begin{cases}
\lambda d_{(j,k), (j'k')},& \text{if } d = d_w\\
(1-\lambda)  d_{(j,k), (j', k')},              & \text{if } d = d_b\\
\end{cases}
\end{equation}

<!-- The maximum weighted pairwise distances are defined as: -->
<!-- $$MEPD = max_{j, j', k, k'}(d*_{(j,k), (j', k')}) -->
<!-- \forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$ -->
<!-- where,  -->
